Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
Update text related to PP plot

% Show injection pp plot
We summarize the result of this injection-recovery campaign in
Fig.~\ref{fig:ppplot}. This shows the cumulative distribution over injections
of the quantile at which the true value lies in the marginalized distribution
of each parameter. The shaded band denotes the 95\%-confident variation
expected from draws from a uniform distribution with the same number of events.
We can see that most of the measured curves lie within this band, showing that
our inference results agree well with a uniform distribution. There is a small
deviation from uniformity for the secondary spin $\chi_2$, which is
not alarming given that we are computing the quantile for 11 parameters.  This
is what we expect if our pipeline is working as expected.

To further quantify how well our result agrees with a uniform distribution, we
can compute the Kolmogorov-Smirnov $p$-values for each marginalized
distribution \cite{}.  A low $p$-value (with a threshold often
chosen to be $p = 0.05$) could indicate that our result is in tension with a uniform
distribution. The $p$-values obtained for each parameter are shown in the
legend of Fig.~\ref{fig:ppplot}. Most of them are well above the $p = 0.05$
threshold, except for $\chi_2$, which is mildly below the threshold. Once
again, assuming these $p$-values are drawn from a uniform distribution, given
11 draws (the number of parameters in our inference), it is not abnormal to
have one of the parameters lying slightly outside the threshold. To assess
whether this is expected, we can compute the combined $p$-value for these 11
parameters, and find it to be $p = 0.47$.  This shows our inference pipeline
performs properly on simulated data at a similar level as standard tools
\cite{Veitch:2014wba,Romero-Shaw:2020owr}.

>>>>

% Show injection pp plot
We summarize the result of this injection-recovery campaign in
Fig.~\ref{fig:ppplot}. This shows the cumulative distribution over injections
of the quantile at which the true value lies in the marginalized distribution
of each parameter. The shaded band denotes the 95\%-confident variation
expected from draws from a uniform distribution with the same number of events.
We can see that most of the measured curves lie within this band, showing that
our inference results agree well with a uniform distribution.

To further quantify how well our result agrees with a uniform distribution, we
can compute the Kolmogorov-Smirnov $p$-values for each marginalized
distribution \cite{}.  A low $p$-value (with a threshold often
chosen to be $p = 0.05$) could indicate that our result is in tension with a uniform
distribution. The $p$-values obtained for each parameter are shown in the
legend of Fig.~\ref{fig:ppplot}. Most of them are well above the $p = 0.05$
threshold, except for $\psi$, which is close to the threshold. Once
again, assuming these $p$-values are drawn from a uniform distribution, given
11 draws (the number of parameters in our inference), it is not abnormal to
have one of the parameters lying slightly outside the threshold. To assess
whether this is expected, we can compute the combined $p$-value for these 11
parameters, and find it to be $p = 0.70$.  This shows our inference pipeline
performs properly on simulated data at a similar level as standard tools
\cite{Veitch:2014wba,Romero-Shaw:2020owr}.
